MS_CNuptake.Rmd

### 2023-06-18 MS_CNuptake.Rmd
correct caption

final1 <- ggplot() +xlim(8,30)+geom_line(data = subset(fits_tg,plt=="Measurement"), aes(Tg_a, visregFit, group=plt, color=plt),size=4)+geom_line(data = fits_tg, aes(Tg_a, visregFit, group=plt, color=plt),size=1) +theme_classic()+theme(text = element_text(size=20),legend.position="none")+  geom_ribbon(data = bp1a$fit,aes(Tg_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+scale_colour_manual(values=c(Measurement="black",CABLE="pink",ISAM="red",ISBA="#339999",JULES="#663399",LPJ="#0066CC",ORCHIDEE="#FF9933",ORCHICNP="cyan",SDGVM="yellow",CLASS="brown",CLM="darkgoldenrod",JSBACH="burlywood1",LPX="darkgreen"))+labs(y = ~paste(BP, " (g C m"^-2," yr"^-1,")"))+xlab("Tg (°C)")
final2 <- ggplot()+xlim(5.5,6.3)+geom_line(data = subset(fits_PPFD,plt=="Measurement"), aes(PPFD_a, visregFit, group=plt, color=plt),size=4) +geom_line(data = fits_PPFD, aes(PPFD_a, visregFit, group=plt, color=plt),size=1) + ylab(" ")+theme_classic()+theme(text = element_text(size=20),legend.position="none")+geom_ribbon(data = bp1b$fit,aes(PPFD_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+ scale_colour_manual(values=c(Measurement="black",CABLE="pink",ISAM="red",ISBA="#339999",JULES="#663399",LPJ="#0066CC",ORCHIDEE="#FF9933",ORCHICNP="cyan",SDGVM="yellow",CLASS="brown",CLM="darkgoldenrod",JSBACH="burlywood1",LPX="darkgreen"))+xlab(~paste("ln gPPFD (", mu, "mol m"^-2," s"^-1, ")"))
final3 <- ggplot()+xlim(-0.8,1) +geom_line(data = subset(fits_vpd,plt=="Measurement"), aes(vpd_a, visregFit, group=plt, color=plt),size=4)+geom_line(data = fits_vpd, aes(vpd_a, visregFit, group=plt, color=plt),size=1) + ylab(" ") +theme_classic()+theme(text = element_text(size=20),legend.position="none")+ geom_ribbon(data = bp1c$fit,aes(vpd_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+scale_colour_manual(values=c(Measurement="black",CABLE="pink",ISAM="red",ISBA="#339999",JULES="#663399",LPJ="#0066CC",ORCHIDEE="#FF9933",ORCHICNP="cyan",SDGVM="yellow",CLASS="brown",CLM="darkgoldenrod",JSBACH="burlywood1",LPX="darkgreen"))+xlab("ln D (kPa)")

#show legend
final1_legend <- ggplot() +geom_line(data = fits_PPFD, aes(PPFD_a, visregFit, group=plt, color=plt),size=2) + xlab("ln PPFD") + ylab(" ")+theme_classic()+theme(text = element_text(size=20))+
  scale_colour_manual(" ",values=c(Measurement="black",CABLE="pink",ISAM="red",ISBA="#339999",JULES="#663399",LPJ="#0066CC",ORCHIDEE="#FF9933",ORCHICNP="cyan",SDGVM="yellow",CLASS="brown",CLM="darkgoldenrod",JSBACH="burlywood1",LPX="darkgreen"), 
                      labels = c("Our model","CABLE","ISAM","ISBA","JULES","LPJ","ORCHIDEE","ORCHICNP","SDGVM","CLASS","CLM","JSBACH","LPX"))

>>>>

final1 <- ggplot() +xlim(8,30)+geom_line(data = subset(fits_tg,plt=="Measurement"), aes(Tg_a, visregFit, group=plt, color=plt),size=4)+geom_line(data = fits_tg, aes(Tg_a, visregFit, group=plt, color=plt),size=1) +theme_classic()+theme(text = element_text(size=20),legend.position="none")+  geom_ribbon(data = bp1a$fit,aes(Tg_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+scale_colour_manual(values=c(Measurement="black",CABLE="pink",ISAM="red",ISBA="#339999",JULES="#663399",LPJ="#0066CC",ORCHIDEE="#FF9933",ORCHICNP="cyan",SDGVM="yellow",CLASS="brown",CLM="darkgoldenrod",JSBACH="burlywood1",LPX="darkgreen"))+labs(y = ~paste(BP, " (g C m"^-2," yr"^-1,")"))+xlab("Tg (°C)")

final2 <- ggplot()+xlim(5.5,6.3)+geom_line(data = subset(fits_PPFD,plt=="Measurement"), aes(PPFD_a, visregFit, group=plt, color=plt),size=4) +geom_line(data = fits_PPFD, aes(PPFD_a, visregFit, group=plt, color=plt),size=1) + ylab(" ")+theme_classic()+theme(text = element_text(size=20),legend.position="none")+geom_ribbon(data = bp1b$fit,aes(PPFD_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+ scale_colour_manual(values=c(Measurement="black",CABLE="pink",ISAM="red",ISBA="#339999",JULES="#663399",LPJ="#0066CC",ORCHIDEE="#FF9933",ORCHICNP="cyan",SDGVM="yellow",CLASS="brown",CLM="darkgoldenrod",JSBACH="burlywood1",LPX="darkgreen"))+xlab(~paste("ln gPPFD (", mu, "mol m"^-2," s"^-1, ")"))

final3 <- ggplot()+xlim(-0.8,1) +geom_line(data = subset(fits_vpd,plt=="Measurement"), aes(vpd_a, visregFit, group=plt, color=plt),size=4)+geom_line(data = fits_vpd, aes(vpd_a, visregFit, group=plt, color=plt),size=1) + ylab(" ") +theme_classic()+theme(text = element_text(size=20),legend.position="none")+ geom_ribbon(data = bp1c$fit,aes(vpd_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+scale_colour_manual(values=c(Measurement="black",CABLE="pink",ISAM="red",ISBA="#339999",JULES="#663399",LPJ="#0066CC",ORCHIDEE="#FF9933",ORCHICNP="cyan",SDGVM="yellow",CLASS="brown",CLM="darkgoldenrod",JSBACH="burlywood1",LPX="darkgreen"))+xlab("ln D (kPa)")

#show legend
final1_legend <- ggplot() +geom_line(data = fits_PPFD, aes(PPFD_a, visregFit, group=plt, color=plt),size=2) + xlab("ln PPFD") + ylab(" ")+theme_classic()+theme(text = element_text(size=20))+
  scale_colour_manual(" ",values=c(Measurement="black",CABLE="pink",ISAM="red",ISBA="#339999",JULES="#663399",LPJ="#0066CC",ORCHIDEE="#FF9933",ORCHICNP="cyan",SDGVM="yellow",CLASS="brown",CLM="darkgoldenrod",JSBACH="burlywood1",LPX="darkgreen"), 
                      labels = c(Measurement="Our model",CABLE="CABLE",ISAM="ISAM",ISBA="ISBA",JULES="JULES",LPJ="LPJ",ORCHIDEE="ORCHIDEE",ORCHICNP="ORCHICNP",SDGVM="SDGVM",CLASS="CLASS",CLM="CLM",JSBACH="JSBACH",LPX="LPX"))
